Update and evaluation of the ozone dry deposition in the Oslo~CTM3 v1.0

### 2019-06-26 version_2/response_version_1_rc2.tex

% Authors' response
\documentclass{scrartcl}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
%\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{xcolor}
\usepackage{url}
\usepackage{multirow}
\usepackage{graphicx}
\usepackage{hyperref}
\thispagestyle{empty}

\begin{document}
\section*{Authors' response}
To gmd-2019-21 referee\#2 David Simpson (10 Apr 2019):
We apologize for the confusion the misuse of the terms \emph{EMEP} and \emph{EMEP scheme} may have caused. We evaluated the major concerns raised in the review and found them severe enough that we have to revise our model and repeat the model experiments to address all concerns. Nevertheless, we will respond to all of the questions and concerns in more detail in the following.

\section{Major points}
\begin{itemize}
\item {\color{blue} Mosaic formulation:}
  \begin{itemize}
  \item {\color{blue} CTM3 claims to implement a mosaic approach, but instead of calculating deposition
rates over each land-cover, and then aggregating using Eqn.3, CTM3 seems to perform the following steps:
\begin{align}
  \label{eq:ra}
  R_a &= \frac{u_z}{u^2_*}\\
  \label{eq:Gsto}
  \overline{Gs^i_g(z)} &= \Sigma^N_{k=1} f_k \times Gs^i_{g,k}(z)\\
  \label{eq:Gns}
  \overline{Gns^i_g(z)} &= \Sigma^N_{k=1} f_k \times Gns^i_{g,k}(z)
\end{align}
As far as I can tell from the text, $R_a$ is calculated once, with the same value of $u_*$ for all land-covers. The CTM3 $R_b$ calculation seems to also use the same $u_*$ over different land-covers, except over sea where a more sophisticated scheme is used. Equations 2--3 above are equivalent to Eqns (22) and (26) from the manuscript. Now I am puzzled however as to how all this is put together. Do they use:
\begin{equation}
  G_c = \mathrm{LAI} \cdot \overline{Gs^i_g(z)} + \overline{Gns^i_g(z)}
\end{equation}
  }
    Thank you very much for your detailed account of the \emph{mosaic approach}. It is correct that we use Eq.~(\ref{eq:Gsto}) and Eq.~(\ref{eq:Gns}). As pointed out, we have not properly indicated the weighted mean in Eq.~(22) and Eq.~(29) in the manuscript. Additionally, there is also a typo in Eq.~(13) and Eq.~(22) ($G_\mathrm{sto}$ should have been $g_\mathrm{sto}$). Eq.~(22) should have read as follows:
    \begin{equation}
      \overline{g^\mathrm{m}_\text{sto}} = \sum_{n=0}^{N} f_{\text{L}, n}\cdot g^\text{m}_{\text{sto}, n}
    \end{equation}    
    All is put together in Eq.~(13):
    \begin{equation}
      \label{eq:Gsto_corr}
      G_c = \mathrm{LAI} \cdot \overline{g^\mathrm{m}_\mathrm{sto}} + \overline{G_\mathrm{ns}}
    \end{equation}
    We acknowledge that Eq.~(13) should not proceed the other equations and that this might have caused additional confusion.

@@

  \item {\color{blue} In any case, I think this approach has serious problems. Why average first for $G_s$ and then for $G_{ns}$ , when it is the fluxes ($F_k$ , or $V^i_{g,k}(z_\mathrm{ref}) \times \chi^i_\mathrm{avg}(z_\mathrm{ref})$) which need to be averaged? I also do not understand why they would use the same $u_*$ and $R_a$ for all land-covers. I think the authors need to make a case for their approach, or change it.}
    We have discussed the concerns raised within this comment and found that we have indeed made a mistake in our implementation of the \emph{mosaic approach} which forces us to revise our model and repeat the model experiments.
  \end{itemize}

\item {\color{blue} Calculation of $R_a$:}
  \begin{itemize}
  \item {\color{blue} $R_a$ in CTM3 appears to be calculated just once, and from a height of 8\,m. This means
that there is no consistency between the $R_a$ term and the underlying surface, which is
clearly wrong. The similarity equation for $R_a$ given in their Eqn~(2) is very standard and has been
used for decades (Garratt 1992). As pointed out by Ref~1, the equation as given has
errors.}
Eq.~(2) in our manuscript is indeed erroneous. The correct equation is (e.g., Erisman, 1994):
\begin{equation}
  R_a = \frac{1}{\kappa u_*}\left[{\ln{\left(\frac{z-d}{z_0}\right)}-\Psi_m\left(\frac{z-d}{L}\right)+\Psi_m\left(\frac{z_0}{L}\right)}\right].
  \label{eq:aero_res}
\end{equation}

\item {\color{blue} The correct equation will not give negative values unless presented with wrong
inputs, and I suspect that that is what has happened. It is actually difficult to tell what
was tested from the manuscript though, since they state simply that $d$ is ’typically 0.7\,m’.
Did they use $d$ properly, consistent with the underlying land-cover and its $z_0$? Did
they assume that their 8\,m meteorology was at a physical height of 8\,m, or at $d + 8\,\mathrm{m}$.
If the latter, which $d$?}
  At that point, it is indeed neither clear from the manuscript nor from our internal documentation. The assumption that Eq.~(2) (in the manuscript) would become negative, was most likely based on a wrong form of the integrated stability function $\Psi_m$.

@@

  Given $z = z_\mathrm{ref} = 8\,\mathrm{m}$ and $d = 0.7\cdot 1\,\mathrm{m}$, it is right that neither the correct Eq.~(\ref{eq:aero_res}) nor the erroneous equation will result in negative $R_a$. The statement "$d$ is ’typically 0.7\,m’" is a typo. We correct: \emph{"[...] typically $d = 0.7\cdot h(N,\mathrm{lat})\,\mathrm{m}$ for vegetation other than forests [...]"}.

  Correction note: The average height of the lowermost model level is actually $20\,\mathrm{m}$ ($10\,\mathrm{m}$ for mid-level).

\item {\color{blue} Lines 19--30 of this section explain the Monteith alternative, but in a rather confusing
way. For example, when is $z_0$ ever zero, as stated on line 23, or why does $\partial_z R_a \rightarrow R_a $
for finite $z$? (I know what they intend to say, but it isn’t at all clear.)}
  The referee is right. The text and derivation of the Monteith relation is confusing and also erroneous. If we do not implement Eq.~(\ref{eq:aero_res}), we will elaborate on this in a revised version of the manuscript: \emph{"
\begin{equation}
  \Phi_{Q_\text{sensible}} = \rho_\text{air}\,c_P \cdot \frac{\Delta T}{R_{a, H}}.
  \label{eq:sens_heat}
\end{equation}
Herein, $\rho_\text{air}$ is the air density, $c_P$ the specific heat at constant pressure $P$, $R_{a, H}$ is the diffusion resistance to sensible heat between surface and the reference height $z$, and $\Delta T$ is the difference between the surface temperature $T_0$ and the temperature at a reference height $T_z$. From the eddy diffusion theorem, a similar formulation can be derived
\begin{equation}
  \Phi_{Q_\text{sensible}} = \rho_\text{air}\,c_P \cdot \frac{\partial T}{\partial u} \cdot u_*^2.
  \label{eq:eddy_theo}
\end{equation}
For finite $z$, $\partial T \rightarrow \Delta T$.
  "}

\item {\color{blue} In any case, here
the authors end up with a stability-independent equation for $R_a$, without mentioning or
discussing that fact.}
  In the revision of the model, we are going to implement the stability dependent $R_a$ following Eq.~(\ref{eq:aero_res}).

@@

  Regarding the three figures with respect to ocean in the supplementary material: The reason for these is that we found some "legacy code" in the model (linear fit to dynamic viscosity of air $\mu(T)$) after we had finished the implementation of the new dry deposition scheme, run the experiments, and done the analysis on these. We had to verify that this had no significant influence on the results.

\item {\color{blue} Use of the term 'EMEP scheme'?: Sect. 3 discusses the comparisons of $V_g$ in terms of ’EMEP scheme’ versus
  ’Wesely scheme’, and sensitivity tests are named e.g. ’EMEP\_offlight’. As noted above
the scheme implemented in CTM3 is very different to that implemented in the EMEP
model, so this is very misleading. Please rename your scheme to something else.
I am worried that readers might get the impression that it is the EMEP scheme which
is being tested here, but it certainly is not. [...]}
  We apologize for the misleading naming of the new dry deposition scheme in the Oslo~CTM3 which is (partly) based on the formulations in the publication the referee refers to as \emph{S2012}. By no means have we meant to offend any of the original authors of the EMEP/MSC-W model nor intended to misguide the readers. We will rename the revised scheme appropriately ($\rightarrow$\emph{mOSaic scheme}).

\item {\color{blue} Reproduction of material from S2012:}
  \begin{itemize}
  \item {\color{blue} As far as I can see, Table S1, S2 and S3 are taken directly from S2012, with no change to parameters. It is not usual to copy tables from the work of other authors in this way.
    Just refer to S2012 (and give Table number as help).}
    We will follow this advice and refer to the tables in S2012 accordingly.

  \item {\color{blue} Many of the equations are from S2012, and many not. I would like the authors to
    make this very explicit, so that readers are not confused as to what comes from EMEP,
    and what has changed for CTM3.}
    We are going to elaborate on this matter in a revised version and refer to our equations' sources more properly.
  \end{itemize}
\end{itemize}
\section{Minor points}
\begin{itemize}
\item {\color{blue}P1 L22. Isn’t $\mathrm{H_2O}$ the most important greenhouse gas? (Say anthropogenic
  GHG perhaps?)}
  Thank you for pointing this out. We follow the advice and write: \emph{"[...] ozone is a potent anthropogenic greenhouse gas [...]"}
\item {\color{blue}P2 L3. The Wilson ref only concerns Europe, and its focus on the 95th percentile can hide trends
  found at higher percentiles (e.g. Simpson et al. 2014). A better ref would be Fleming et al. (2018) or Mills et al. (2018a). By the way, the most recent calculation on food security (using flux approaches) is now Mills et al. (2018b).}

@@

\item {\color{blue}P5 L5. I would add Emberson et al. (2000a) and Tuovinen et al. (2004) to
the list of EMEP refs here, since this was the first publication of the methods that
have more or less been used until today.}
  We have added the references regarding the EMEP MSC-W model. \emph{"[...] we mainly follow Simpson et al. (2012) in their description of dry deposition used in the European Monitoring and Evaluation Programme (EMEP) MSC-W model (see also, Emberson et al., 2000; Simpson et al., 2003; Tuovinen et al., 2004;), [...]"}

\item {\color{blue}P7, notation. In S2012 and EMEP generally, we use upper-case G and R to refer
to canopy-scale (bulk) variables, and lower-case for leaf-scale. Thus, in EMEP
we would have $G_\mathrm{sto} = LAI g_\mathrm{sto}$. Here the authors seem to mix upper and lower
case between their equations (13) and (14).}
  We have indeed mixed up the cases here.

\item {\color{blue}P7 Eqn (13). Is LAI one-sided, 2-sided, projected .... define.}
  LAI is one-sided taken from ISLSCP2 FASIR. We add this to the sentence: \emph{"[...] $\text{LAI}$ is the one-sided leaf area index taken from ISLSCP2 FASIR [...]"}

\item {\color{blue}P8 L1. S2012 do not suggest using depths lower than 1\,m. We use SMI3 which
  is from 28-100 cm.}
Thank you for the clarification. This may have been a misunderstanding on our side. Since we have to repeat our simulations, we will choose the appropriate SWVL from the start.

\item {\color{blue}P8 L2. Why did you choose to use the surface (0--7\,cm) soil moisture?}
  Initially we choose 0--7\,cm due to the original scope of this work within our research project, in which we study ozone concentrations and uptake by plants in boreal regions where the soil columns are expected to be more shallow then, e.g., at mid-latitudes. We expect the stomatal conductance in these environments to be more sensitive to precipitation. Using the actual water availability to vegetation, would be better, but this is not feasible without a proper land surface model.

@@

\item {\color{blue}P9 Eqn (26). Say 1st and 2nd, not I. and II.}
  We follow the advise regarding Eq.~(26) and also change Table~1 accordingly.

\item {\color{blue}P9 Eqn (27). This equation is a modification of Erisman’s original (1994) formulation, so explain that.}
  We follow the advise and write: \emph{"The in-canopy resistance $R_\text{inc}$ (Erisman et al., 1994) is then modified with respect to each (vegetated) land type $N$ [...]"} {\bfseries ToDo -- To Amund: Were does this modification come from?}

\item {\color{blue}P10 L12. Be explicit that this statement refers to S2012. The current EMEP
  model uses different heights for e.g. tropical vegetation.}
  We follow this advice and write: \emph{"The vegetation height $h(N, \text{lat})$ as described by Simpson et al. (2012) [...]"}

\item {\color{blue}P11 Sect 2.2. I also found this aerosol section confusing. Eqn (30) is from S2012,
and so is the factor 0.008.SAI/10 used in Eqn (33), but here new $a_1$ coefficients
are defined. Did the ’aerosol microphysic model’ referred to also mix equations
in this way? Is there any publication as to the reliability of this method?}
  The $a_1$ coefficients were calculated from deposition velocities taken from the Oslo~CTM2 (\href{http://folk.uio.no/mariantl/osloctm3/history.html}{Oslo~CTM2 list of publications}). We meant to use this new scheme for aerosols in the Oslo~CTM3, but as of now it has not been evaluated and is actually not used. Hence, we will remove this section from the paper and add: \emph{"In addition to the gaseous species, Simpson at al. (2012) also modify aerosol deposition velocities, namely black carbon (BC) and organic carbon (OC), sulfuric aerosols ($\mathrm{SO_4}$, $\mathrm{MSA}$) and secondary organic aerosols (SOA), but we have not updated our model with respect to these."}.

### 2019-06-26 DryDep.tex
First version of revised model description.

As displayed in Eq.~(\ref{eq:drydep_velo}), the dry deposition computation is subdivided into contributions from three different resistances. The main idea of a mosaic approach is to calculate these resistences dependent on the fraction of land surface types $k$ in each grid cell: $R_a^k$,$R^{i,k}_b$, and $R^{i,k}_c$.

\subsubsection{Aerodynamic resistance}
\label{subsubsec:Ra}
In general, the aerodynamic resistance is describing the turbulent transport of any substance down to the surface. To derive $R_a^k$, \citet{WASP:Simpson2003,ACP:Simpson2012} compute a local friction velocity at reference height $z_\mathrm{ref}$ \citep[Eq.~(52),][]{ACP:Simpson2012}
\begin{equation}
  u_*^k = \frac{\overline{u}(z_\mathrm{ref})\cdot\kappa}{\ln{(\frac{z_\mathrm{ref}-d_k}{z_0^k})}-\Psi_m(\frac{z_\mathrm{ref}-d_k}{L})+\Psi_m(\frac{z_0^k}{L})},
  \label{eq:local_fric_vel}
\end{equation}
with an average wind speed $\overline{u}(z_\mathrm{ref})$, the K\'{a}rm\'{a}n constant $\kappa = 0.40$, the integrated stability equation for momentum $\Psi_m$ \citep[e.g.,][]{Garratt1992}, a grid average Obukhov length $L$, deplacement height $d_k$, and surface height $z_0^k$ ($d_k=0.78\cdot h_k(\mathrm{lat})$, $z_0^k=0.07\cdot h_k(\mathrm{lat})$ for forests, $d_k=0.7\cdot h_k(\mathrm{lat})$, $z_0^k=0.1\cdot h_k(\mathrm{lat})$ for vegetation other than forests). We have chosen a model level where $\overline{z}_\mathrm{ref}\approx 45\,\unit{m}$. From Eq.~(\ref{eq:local_fric_vel}), a local Obukhov length $L_k$ is found \citep[Eq.~(8),][]{ACP:Simpson2012}:
\begin{equation}
  L_k = - \frac{\rho c_p T_\mathrm{2m} u_*^k}{\kappa g H}.
\end{equation}
Herein, $H$ is the sensible heat flux, $g$ is the standard gravitational acceleration, $c_p$ the specific heat capacity, and $T_{2m}$ the $2\,\unit{m}$ temperature. With this we get \citep[Eq.~(8.8),][]{WASP:Simpson2003}
\begin{equation}
  R_a^k = \frac{1}{\kappa u_*^k}\left[{\ln{\left(\frac{z_\mathrm{ref}-d_k}{z_0^k}\right)}-\Psi_h\left(\frac{z_\mathrm{ref}-d_k}{L_k}\right)+\Psi_h\left(\frac{z_0^k}{L_k}\right)}\right],
\end{equation}
with the integrated stability equation for heat $\Psi_h$.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Quasi-laminar layer resistance}
\label{subsubsec:Rb}
The quasi-laminar layer resistance $R_b^{i,k}$ is species specific and differs only over land and ocean surfaces.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Over land, we use \citep[Eq.~(53),][]{ACP:Simpson2012}
\begin{equation}
  R_b^{i,k} = \frac{2}{\kappa u_*} \cdot \left(\frac{\text{Sc}_i}{\text{Pr}}\right)^{\frac{2}{3}},
  \label{eq:Rb}
\end{equation}
wherein $\text{Pr}$ is the Prandtl number (typically 0.72 for air and other gases) and $\text{Sc}_i$ is the Schmidt number for a gas $i$. Eq.~(\ref{eq:Rb}) differs from a similar formulation in \citet{ACP:Seinfeld2006} by a factor of roughly $1.25$. From $\text{Sc}_i = \nu/D_i$, with the kinematic viscosity of air $\nu$, we derive a Schmidt number in water equivalent:
\begin{equation}
  \text{Sc}_i = \frac{D_\chem{H_2O}}{D_i} \cdot \text{Sc}_\chem{H_2O},
\end{equation}
with the molecular diffusivity for any gas $D_i$, the Schmidt number of water ($\text{Sc}_\chem{H_2O}=0.6$) and its molecular diffusivity ($D_\chem{H_2O}=0.21\cdot10^{-4}\,\unit{m^2\,s^{-1}}$). The used ratios $D_\chem{H_2O}/D_i$ are taken from \citet[][Table S18]{ACP:Simpson2012}.\\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Over ocean, we use \citep[Eq.~(54),][]{ACP:Simpson2012}
\begin{equation}
  R_b^i = \frac{1}{\kappa u_*}\cdot\ln\left({\frac{z_0}{D_i}\cdot \kappa u_*}\right)
\end{equation}
with an imposed lower threshold of $10\,\unit{s\,m^{-1}}$ and an upper limit of $1000\,\unit{s\,m^{-1}}$. The computation of roughness length $z_0$ over ocean is divided into a \emph{calm} and a \emph{rough} sea case, with a threshold of $3\,\unit{m\,s^{-1}}$. For calm sea, we apply the following upper limit \citep[][with a slightly higher coefficient of $0.135$]{Hinze1975,Garratt1992}
\begin{equation}
  z_0^\text{calm} = \text{min}\left\{2\cdot10^{-3}, 0.135 \cdot \frac{\nu}{u_*}\right\}.
\end{equation}
The kinematic viscosity of air $\nu$ herein can be computed from 
\begin{equation}
  \nu = \frac{\mu}{\rho} = \frac{\mu(T)}{\frac{P_0}{T\cdot R_\text{air}}}.
  \label{eq:kinematic_viscosity}
\end{equation}
For the temperature dependent dynamic viscosity of air $\mu(T)$, we chose a linear fit to Sutherland's law through the origin within the temperature range $\{T \in \mathbb{R} | (243.15 < T < 313.15)\,\unit{K}\}$: $\mu(T) = 6.2\cdot 10^{-8}\,\unit{kg\,m^{-1}\,s^{-1}\,K^{-1}} \cdot T$. But despite its rough accuracy, we found that the choice of $\mu(T)$ has no effect on $\overline{R}_b^{i,k}$ (Supplement~S.1: Figs.~S1--S2). In Eq.~(\ref{eq:kinematic_viscosity}), $\rho$ is substituted by the air density using the ideal gas law. $P_0$ is the surface pressure, as $T$ the $2\,\unit{m}$ temperature is chosen, and $R_\text{air}$ is the universal gas constant for air.
The rough sea case follows the method of \citet{QJRMS:Charnock1955,JPO:Wu1980}:
\begin{equation}
  z_0^\text{rough} = \text{min}\left\{2\cdot10^{-3}, 0.018 \cdot \frac{u^2_*}{g}\right\}
\end{equation}
with a gravitational acceleration $g = 9.836\,\unit{m\,s^{-2}}$. The allowed maximum roughness length in both cases is set to $2\,\unit{mm}$. Since the $z_0$ computed with this parameterization are rather small ($0 < z_0^\text{calm} < 1\cdot 10^{-4}\,\unit{m}$, $0 < z_0^\text{rough} < 2 \cdot 10^{-3}\,\unit{m}$), $R^i_b$ is set to its lower limit of $10\,\unit{s\,m^{-1}}$ in about $91\,\unit{\%}$ of all cases (see Supplement~S.1: Fig.~S3). 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Surface resistance}
\label{subsubsec:Rc}
The surface resistance consists of both, stomatal and non-stomatal resistances. When computing gridbox averages, we use the sum of conductances (deposition velocities)
\begin{equation}
  G_c = \text{LAI} \cdot g_\text{sto} + G_\text{ns}, 
\end{equation}
wherein $\text{LAI}$ is the one-sided leaf area index taken from ISLSCP2 FASIR (zero for non-vegetated surfaces), $G_\text{sto}$ the stomatal conductance, and $G_\text{ns}$ the non-stomatal conductance.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\subsubsection*{Stomatal conductance}
The stomatal conductance is a measure of the rate of \chem{CO_2} exchange and evapotranspiration through the stomata of a leaf. There are several environmental conditions affecting the opening and closing of the stomata and hence their capability of respiration (e.g., light, available water, etc.). Stomata sluggishness, a state in which the stomata can no longer fully close, has been reported as ozone induced damage \citep{SR:Hoshika2015}, but is not taken into account in our formulation. To reflect part of the underlying mechanism, the stomatal conductance $G_\text{sto}$ in the mOSaic scheme is computed using a multiplicative ansatz that is also explained in much detail in \citet{ICP:MappingManual2017}:
%
\begin{equation}
  G_\text{sto} = g^\text{m}_\text{max} \cdot f_\text{phen} \cdot f_\text{light} \cdot \max{\left\{f_\text{min}, f_T \cdot f_D \cdot f_\text{SW}\right\}}.
  \label{eq:stomatal}
\end{equation}
%
The factors herein are normalized and vary within the range $0-1$. They account for leaf phenology ($f_\text{phen}$), light ($f_\text{light}$), temperature ($f_T$), water vapor pressure deficit ($f_D$), and soil water content ($f_\text{SW}$).

The temperature adjustment $f_T$ of plants is computed from
%
\begin{equation}
  f_T = \frac{T_\text{2m}-T_\text{min}}{T_\text{opt}-T_\text{min}} \cdot \left(\frac{T_{\text{max}}-T_\text{2m}}{T_{\text{max}}-T_\text{opt}}\right)^\beta, 
\end{equation}
with $\beta = \frac{T_\text{max}-T_\text{opt}}{T_\text{opt}-T_\text{min}}$. The parameters $T_\text{min}$, $T_\text{max}$ and $T_\text{opt}$ are tabulated for various land surface types. All parameters used in the mOSaic scheme can be found in the supplementary to \citet[][Tables S16, S19]{ACP:Simpson2012}. Since $f_T$ turns negative outside its range defined by $T_\text{min}$, $T_\text{max}$, we impose a lower limit of $0.01$.

@@

The penalty factor with respect to available soil water ($\text{SW}$) $f_\text{SW}$ is defined as 
%
\begin{equation}
  f_\text{SW} =
  \begin{cases}
    1 & \quad \emph{if} \quad \text{SW} \geq 0.5,\\
    2 \cdot \text{SW}  & \quad \emph{if} \quad \text{SW} < 0.5.
  \end{cases}
\end{equation}
\citet{ACP:Simpson2012} suggest using SW of soil depths below $1\,\unit{m}$ (SWVL4 in OpenIFS). Throughout most of our simulations (Section~\ref{sec:eval}), we have, however, used the soil water contained in the top layer (SWVL1, $0-7\,\unit{cm}$), which makes the canopy conductance more sensitive to precipitation than it would be otherwise.

>>>>

As displayed in Eq.~(\ref{eq:drydep_velo}), the dry deposition computation is subdivided into contributions from three different resistances. The main idea of a mosaic approach is to calculate these resistances separately for each land surface type $k$ in each grid cell: $R_a^k$,$R^{i,k}_b$, and $R^{i,k}_c$.
The grid cell average dry deposition velocity $\overline{v}_\mathrm{DD}^{i}$ is then defined by weighting each individual $v_\mathrm{DD}^{i,k}$ by the corresponding land fraction factor $f_k$:
\begin{equation}
  \overline{v}_\mathrm{DD}^{i} = \sum_k{f_k v_\mathrm{DD}^{i,k}}
  \label{eq:ddep_velo_wa}
\end{equation}

\subsubsection{Aerodynamic resistance}
\label{subsubsec:Ra}
In general, the aerodynamic resistance is describing the turbulent transport of any substance down to the surface. To derive $R_a^k$, we follow \citet{WASP:Simpson2003,ACP:Simpson2012} and compute a local friction velocity at reference height $z_\mathrm{ref}$ \citep[Eq.~(52),][]{ACP:Simpson2012}
\begin{equation}
  u_*^k = \frac{\overline{u}(z_\mathrm{ref})\cdot\kappa}{\ln{(\frac{z_\mathrm{ref}-d_k}{z_0^k})}-\Psi_m(\frac{z_\mathrm{ref}-d_k}{L})+\Psi_m(\frac{z_0^k}{L})},
  \label{eq:local_fric_vel}
\end{equation}
with the average wind speed $\overline{u}(z_\mathrm{ref})$ at reference height, the K\'{a}rm\'{a}n constant $\kappa = 0.40$, the integrated stability equation for momentum $\Psi_m$ \citep[e.g.,][]{Garratt1992}, a grid average Obukhov length $L$, deplacement height $d_k$, and roughness length $z_0^k$ ($d_k=0.78\cdot h_k(\mathrm{lat})$, $z_0^k=0.07\cdot h_k(\mathrm{lat})$ for forests, $d_k=0.7\cdot h_k(\mathrm{lat})$, $z_0^k=0.1\cdot h_k(\mathrm{lat})$ for vegetation other than forests). We have chosen the model level such that $\overline{z}_\mathrm{ref}\approx 45\,\unit{m}$. Using the derived $u_*^k$ from Eq.~(\ref{eq:local_fric_vel}), a local Obukhov length $L_k$ can by obtained with \citep[Eq.~(8),][]{ACP:Simpson2012}:
\begin{equation}
  L_k = - \frac{\rho c_p T_\mathrm{2m} u_*^k}{\kappa g H}.
\end{equation}
Herein, $H$ is the sensible heat flux, $g$ is the standard gravitational acceleration, $c_p$ the specific heat capacity, and $T_{2m}$ the $2\,\unit{m}$ temperature. With these, we get \citep[Eq.~(8.8),][]{WASP:Simpson2003}
\begin{equation}
  R_a^k = \frac{1}{\kappa u_*^k}\left[{\ln{\left(\frac{z_\mathrm{ref}-d_k}{z_0^k}\right)}-\Psi_h\left(\frac{z_\mathrm{ref}-d_k}{L_k}\right)+\Psi_h\left(\frac{z_0^k}{L_k}\right)}\right],
\end{equation}
with the integrated stability equation for heat $\Psi_h$ \citep[e.g.,][]{Garratt1992}. Both integrated stability functions ($\Psi_m$, $\Psi_h$) and corresponding parameters are listed in supplement~S.1.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Quasi-laminar layer resistance}
\label{subsubsec:Rb}
The quasi-laminar layer resistance $R_b^{i,k}$ is species specific and differs over land and ocean surfaces.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Over land, we use \citep[Eq.~(53),][]{ACP:Simpson2012}
\begin{equation}
  R_b^{i,k} = \frac{2}{\kappa u_*} \cdot \left(\frac{\text{Sc}_i}{\text{Pr}}\right)^{\frac{2}{3}},
  \label{eq:Rb}
\end{equation}
wherein $\text{Pr}$ is the Prandtl number (typically 0.72 for air and other gases) and $\text{Sc}_i$ is the Schmidt number for a gas $i$. Eq.~(\ref{eq:Rb}) differs from a similar formulation in \citet{ACP:Seinfeld2006} by a factor of roughly $1.25$. From $\text{Sc}_i = \nu/D_i$, with the kinematic viscosity of air $\nu$, we derive a Schmidt number in water equivalent:
\begin{equation}
  \text{Sc}_i = \frac{D_\chem{H_2O}}{D_i} \cdot \text{Sc}_\chem{H_2O},
\end{equation}
with the molecular diffusivity for any gas $D_i$, the Schmidt number of water ($\text{Sc}_\chem{H_2O}=0.6$) and its molecular diffusivity ($D_\chem{H_2O}=0.21\cdot10^{-4}\,\unit{m^2\,s^{-1}}$). The used ratios $D_\chem{H_2O}/D_i$ are taken from \citet[][Table S18]{ACP:Simpson2012}.\\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Over ocean, we use \citep[Eq.~(54),][]{ACP:Simpson2012}
\begin{equation}
  R_b^i = \frac{1}{\kappa u_*}\cdot\ln\left({\frac{z_0}{D_i}\cdot \kappa u_*}\right)
\end{equation}
with an imposed lower threshold of $10\,\unit{s\,m^{-1}}$ and an upper limit of $1000\,\unit{s\,m^{-1}}$. The computation of roughness length $z_0$ over ocean is divided into a \emph{calm} and a \emph{rough} sea case, with a threshold of $3\,\unit{m\,s^{-1}}$. For calm sea, we apply the following upper limit \citep[][with a slightly higher coefficient of $0.135$]{Hinze1975,Garratt1992}
\begin{equation}
  z_0^\text{calm} = \text{min}\left\{2\cdot10^{-3}, 0.135 \cdot \frac{\nu}{u_*}\right\}.
\end{equation}
The kinematic viscosity of air $\nu$ herein can be computed from 
\begin{equation}
  \nu = \frac{\mu}{\rho} = \frac{\mu(T)}{\frac{P_0}{T\cdot R_\text{air}}}.
  \label{eq:kinematic_viscosity}
\end{equation}
For the temperature dependent dynamic viscosity of air $\mu(T)$, we chose a linear fit to Sutherland's law through the origin within the temperature range $\{T \in \mathbb{R} | (243.15 < T < 313.15)\,\unit{K}\}$: $\mu(T) = 6.2\cdot 10^{-8}\,\unit{kg\,m^{-1}\,s^{-1}\,K^{-1}} \cdot T$. But despite its rough accuracy, we found that the choice of $\mu(T)$ has no effect on $\overline{R}_b^{i,k}$ (Supplement~S.2: Figs.~S1--S2). In Eq.~(\ref{eq:kinematic_viscosity}), $\rho$ is substituted by the air density using the ideal gas law. $P_0$ is the surface pressure, as $T$ the $2\,\unit{m}$ temperature is chosen, and $R_\text{air}$ is the universal gas constant for air.
The rough sea case follows the method of \citet{QJRMS:Charnock1955,JPO:Wu1980}:
\begin{equation}
  z_0^\text{rough} = \text{min}\left\{2\cdot10^{-3}, 0.018 \cdot \frac{u^2_*}{g}\right\}
\end{equation}
with a gravitational acceleration $g = 9.836\,\unit{m\,s^{-2}}$. The allowed maximum roughness length in both cases is set to $2\,\unit{mm}$. Since the $z_0$ computed with this parameterization are rather small ($0 < z_0^\text{calm} < 1\cdot 10^{-4}\,\unit{m}$, $0 < z_0^\text{rough} < 2 \cdot 10^{-3}\,\unit{m}$), $R^i_b$ is set to its lower limit of $10\,\unit{s\,m^{-1}}$ in about $91\,\unit{\%}$ of all cases (see Supplement~S.2: Fig.~S3). 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Surface resistance}
\label{subsubsec:Rc}
The surface resistance consists of both, stomatal and non-stomatal resistances.\\ 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\subsubsection*{Stomatal conductance}
The stomatal conductance is a measure of the rate of \chem{CO_2} exchange and evapotranspiration through the stomata of a leaf. There are several environmental conditions affecting the opening and closing of the stomata and hence the capability of respiration (e.g., light, available water, etc.). Stomata sluggishness, a state in which the stomata can no longer fully close, has been reported as ozone induced damage \citep{SR:Hoshika2015}, but is not taken into account in our formulation. To reflect part of the underlying mechanism, the leaf-level stomatal conductance in the mOSaic scheme is computed using a common multiplicative ansatz \citep{BallBerry1987, ICP:MappingManual2017}:
%
\begin{equation}
  g^k_\text{sto, m} = g^k_\text{max, m} \cdot f^k_\text{phen} \cdot f^k_\text{light} \cdot \max{\left\{f^k_\text{min}, f^k_T \cdot f^k_D \cdot f^k_\text{SW}\right\}}.
  \label{eq:stomatal}
\end{equation}
%
The factors herein are normalized and vary within the range $0-1$ and account for leaf phenology ($f_\text{phen}$), light ($f_\text{light}$), temperature ($f_T$), water vapor pressure deficit ($f_D$), and soil water content ($f_\text{SW}$). All factors differ with land use type $k$. For clarity reasons, we drop this index in the following, as long is it not necessary for the equation.

The temperature adjustment $f_T$ is computed from
%
\begin{equation}
  f_T = \frac{T_\text{2m}-T_\text{min}}{T_\text{opt}-T_\text{min}} \cdot \left(\frac{T_{\text{max}}-T_\text{2m}}{T_{\text{max}}-T_\text{opt}}\right)^\beta, 
\end{equation}
with $\beta = \frac{T_\text{max}-T_\text{opt}}{T_\text{opt}-T_\text{min}}$. The parameters $T_\text{min}$, $T_\text{max}$ and $T_\text{opt}$ are tabulated for various plant functional types. All parameters are taken from Supplementary \citet[][Tables S16, S19]{ACP:Simpson2012}. Since $f_T$ turns negative outside the range defined by $T_\text{min}$, $T_\text{max}$, we impose a lower limit of $0.01$.

@@

The penalty factor with respect to available soil water ($\text{SW}$) $f_\text{SW}$ is defined as 
%
\begin{equation}
  f_\text{SW} =
  \begin{cases}
    1 & \quad \emph{if} \quad \text{SW} \geq 0.5,\\
    2 \cdot \text{SW}  & \quad \emph{if} \quad \text{SW} < 0.5.
  \end{cases}
\end{equation}
SW is evaluated at a soil depths of $0.28-1\,\unit{m}$, which corresponds to SWVL3 in OpenIFS.
